---
title: "Project Outline"
output: html_document
---

```{r}
require(tidyverse)
require(jsonlite)
require(httr)
require(devtools)
require(jsonlite)
require(dplyr)
require(readr)
library(shiny)
library(shinyjs)
library(leaflet)
library(maps)
require(ggmap)

#ny <- read_csv("data/meetup_groupsNYlocation.csv",  col_names = FALSE, col_types = list(col_character(),col_character(),col_integer(),col_character(),col_integer(),col_character(),col_character(),col_character()))
ny <- read_csv("data/meetup_groupsNYlocation.csv",  col_names = FALSE)
ny$lat
ny$lat<-as.numeric(ny$lat)
#Still truncates the number!!!
bo <- read_csv("data/MA.csv", col_names= FALSE)
ch <- read_csv("data/NC.csv", col_names=FALSE)
ha <- read_csv("data/CT.csv", col_names=FALSE)

#Function to rename columns for each dataset
colnames(ny)[1] <- "city"
colnames(ny)[2] <- "group_name"
colnames(ny)[3] <- "created"
colnames(ny)[4] <- "category"
colnames(ny)[5] <- "members"
colnames(ny)[6] <- "details"
colnames(ny)[7] <- "lat"
colnames(ny)[8] <- "long"

colnames(bo)[1] <- "city"
colnames(bo)[2] <- "group_name"
colnames(bo)[3] <- "created"
colnames(bo)[4] <- "category"
colnames(bo)[5] <- "members"
colnames(bo)[6] <- "details"
colnames(bo)[7] <- "lat"
colnames(bo)[8] <- "long"

colnames(ha)[1] <- "city"
colnames(ha)[2] <- "group_name"
colnames(ha)[3] <- "created"
colnames(ha)[4] <- "category"
colnames(ha)[5] <- "members"
colnames(ha)[6] <- "details"
colnames(ha)[7] <- "lat"
colnames(ha)[8] <- "long"

colnames(ch)[1] <- "city"
colnames(ch)[2] <- "group_name"
colnames(ch)[3] <- "created"
colnames(ch)[4] <- "category"
colnames(ch)[5] <- "members"
colnames(ch)[6] <- "details"
colnames(ch)[7] <- "lat"
colnames(ch)[8] <- "long"

#top categories based on membership count
top10 <- function(data) {
  data %>%
    group_by(category, city) %>%
    summarize(members_tot = sum(members), topgroup=max(members))  %>%
    arrange(desc(members_tot)) %>%
    head(10)
}
 chtop10<-top10(data=ch)
 hatop10<-top10(data=ha)
botop10<-top10(data=bo)
nytop10<-top10(data=ny) 
alltop10<-cbind(chtop10, hatop10, botop10, nytop10)
topcatbymember(alltop10)+facet_wrap(~city)
topcatbymember<-function(x){ggplot(data=x, aes(x=reorder(category, members_tot), y=members_tot))+geom_bar(stat="identity", aes(fill=topgroup)) +coord_flip()+ylab("Total Members")+xlab("Category")+scale_fill_continuous(name="top group membership")
}

ggplot(data=chtop10, aes(x=reorder(category, members_tot), y=members_tot))+geom_bar(stat="identity", aes(fill=topgroup)) +coord_flip()+ylab("Total Members")+xlab("Category")+scale_fill_continuous(name="top group membership")

unique(ch$category)                                                                                                 
topcatbymember(chtop10)+ labs(title = "Charlotte top categories by membership")
topcatbymember(botop10)+labs(title = "Boston top categories by membership")
topcatbymember(hatop10)+labs(title = "Hartford top categories by membership")
topcatbymember(nytop10)+labs(title = "NY top categories by membership")

```


```{r}
#creates df topics with number of groups per topic (fix this)
mostgroups<- function(data){
  topics <-data %>% 
  group_by(category) %>% 
  summarise(group_tot = n()) %>% 
  arrange(desc(group_tot));topics %>% 
    head(10)
}

chgroups<-mostgroups(ch)
nygroups<-mostgroups(ny)
bogroups<-mostgroups(bo)
hagroups<-mostgroups(ha)

topcatbygroup<-function(x){ggplot(data=x, aes(x=reorder(category, group_tot), y=group_tot))+geom_bar(stat="identity", aes(fill=group_tot)) +coord_flip()+ylab("Total groups")+xlab("Category")+scale_fill_continuous(name="total groups per category")
}
topcatbygroup(chgroups)+ labs(title = "Charlotte top categories by group number")
topcatbygroup(bogroups)+labs(title = "Boston top categories by group number")
topcatbygroup(hagroups)+labs(title = "Hartford top categories by group number")
topcatbygroup(nygroups)+labs(title = "NY top categories by group number")


```

```{r}


nysocializing <- ny %>% 
  filter(category == "socializing")

nylanguage <- ny %>% 
  filter(category == "language/ethnic identity")

nytech <- ny %>% 
  filter(category == "tech")

nysports <- ny %>% 
  filter(category == "sports/recreation")
```

```{r}
#Hartford


ctsocializing <- ha %>% 
  filter(category == "socializing")

ctlanguage <- ha %>% 
  filter(category == "language/ethnic identity")

cttech <- ha %>% 
  filter(category == "tech")

ctsports <- ha %>% 
  filter(category == "sports/recreation")
```

```{r}
#Boston

bosocializing <- bo %>% 
  filter(category == "socializing")

bolanguage <- bo %>% 
  filter(category == "language/ethnic identity")

botech <- bo %>% 
  filter(category == "tech")

bosports <- bo %>% 
  filter(category == "sports/recreation")
```

```{r}
#Charlotte


chsocializing <- ch %>% 
  filter(category == "socializing")

chlanguage <- ch %>% 
  filter(category == "language/ethnic identity")

chtech <- ch %>% 
  filter(category == "tech")

chsports <- ch %>% 
  filter(category == "sports/recreation")
```


As you can see, the category with the most membership is normally "socializing" in big cities like Charlotte, Boston and New York. Given how at it's core meetup is designed to bring people together over shared interests, it is no wonder that socializing has the highest volume of membership. However, in group total, the cities vary as to what types of groups are most frequently made. In Boston, the majority of the meetups are based around tech, fitting for the startup vibe. In Charlotte and Hartford, the majority of the groups are interestingly about career or business, and in New York, the majority of the meetup groups are socializing groups. The majority of topics have less than 40 dedicated groups. We also wanted to look at where the majority of these groups were located and if there were certain "hubs" for technology. We investigate this question with Shiny. 

#Shiny Time

```{r}
#Template
Aukland <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
Aukland  # Print the map
```

```{r}
#Icons
greenIcon <- makeIcon(
  iconUrl = "https://cdn.rawgit.com/pointhi/leaflet-color-markers/master/img/marker-icon-2x-green.png",
  iconWidth = 25, iconHeight = 41,
  iconAnchorX = 12, iconAnchorY = 41
)

redIcon <- makeIcon(
  iconUrl = "https://cdn.rawgit.com/pointhi/leaflet-color-markers/master/img/marker-icon-2x-red.png",
  iconWidth = 25, iconHeight = 41,
  iconAnchorX = 12, iconAnchorY = 41
)

orangeIcon <- makeIcon(
  iconUrl = "https://cdn.rawgit.com/pointhi/leaflet-color-markers/master/img/marker-icon-2x-orange.png",
  iconWidth = 25, iconHeight = 41,
  iconAnchorX = 12, iconAnchorY = 41
)
```


```{r}
# map of NY with events as category

NY  <- leaflet() %>%
  addTiles() %>%  
  #markers(Hartford)# Add default OpenStreetMap map tiles
  addMarkers(data=nysocializing, popup="social",icon=orangeIcon) %>% 
  addMarkers(data=nylanguage, popup="language",icon=greenIcon) %>% 
  addMarkers(data=nysports, popup="sports",icon=redIcon) %>% 
  addMarkers(data=nytech, popup="tech",)
NY

map <-  get_map(location="newyork",zoom=12,source="google")

ggmap(map) + geom_point(data=ny, aes(x=lat, y=long), alpha=-.3, show.legend = FALSE)
ggmap(map)
```

```{r}
# map of Hartford
hartfordmap  <- leaflet() %>%
  addTiles() %>%  
  #markers(Hartford)# Add default OpenStreetMap map tiles
  addMarkers(data=ctsocializing, popup="social",icon=orangeIcon) %>% 
  addMarkers(data=ctlanguage, popup="language",icon=greenIcon) %>% 
  addMarkers(data=ctsports, popup="sports",icon=redIcon) %>% 
  addMarkers(data=cttech, popup="tech")
hartfordmap
```

```{r}
# map of Boston
bostonmap  <- leaflet() %>%
  addTiles() %>%  
  #markers(Hartford)# Add default OpenStreetMap map tiles
  addMarkers(data=bosocializing, popup="social",icon=orangeIcon) %>% 
  addMarkers(data=bolanguage, popup="language",icon=greenIcon) %>% 
  addMarkers(data=bosports, popup="sports",icon=redIcon)%>% 
  addMarkers(data=botech, popup="tech")
bostonmap
```

```{r}
# map of Charlotte
charlottemap  <- leaflet() %>%
  addTiles() %>%  
  #markers(Hartford)# Add default OpenStreetMap map tiles
  addMarkers(data=chsocializing, popup="social",icon=orangeIcon) %>% 
  addMarkers(data=chlanguage, popup="language",icon=greenIcon) %>% 
  addMarkers(data=chsports, popup="sports",icon=redIcon) %>% 
  addMarkers(data=chtech, popup="tech", clusterOptions = markerClusterOptions())
charlottemap
```
