---
title: "Let's Meetup!"
author: "Victoria and Ian"
date: "12/11/2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

require(tidyverse)
require(jsonlite)
require(httr)
require(devtools)
require(jsonlite)
require(dplyr)
require(readr)
library(shiny)
library(shinyjs)
library(leaflet)
library(maps)
require(ggmap)

ny <- read_csv("data/meetup_groupsNYlocation.csv",  col_names = FALSE)

bo <- read_csv("data/MA.csv", col_names= FALSE)
ch <- read_csv("data/NC.csv", col_names=FALSE)
ha <- read_csv("data/CT.csv", col_names=FALSE)

#Function to rename columns for each dataset
colnames(ny)[1] <- "city"
colnames(ny)[2] <- "group_name"
colnames(ny)[3] <- "created"
colnames(ny)[4] <- "category"
colnames(ny)[5] <- "members"
colnames(ny)[6] <- "details"
colnames(ny)[7] <- "lat"
colnames(ny)[8] <- "long"

colnames(bo)[1] <- "city"
colnames(bo)[2] <- "group_name"
colnames(bo)[3] <- "created"
colnames(bo)[4] <- "category"
colnames(bo)[5] <- "members"
colnames(bo)[6] <- "details"
colnames(bo)[7] <- "lat"
colnames(bo)[8] <- "long"

colnames(ha)[1] <- "city"
colnames(ha)[2] <- "group_name"
colnames(ha)[3] <- "created"
colnames(ha)[4] <- "category"
colnames(ha)[5] <- "members"
colnames(ha)[6] <- "details"
colnames(ha)[7] <- "lat"
colnames(ha)[8] <- "long"

colnames(ch)[1] <- "city"
colnames(ch)[2] <- "group_name"
colnames(ch)[3] <- "created"
colnames(ch)[4] <- "category"
colnames(ch)[5] <- "members"
colnames(ch)[6] <- "details"
colnames(ch)[7] <- "lat"
colnames(ch)[8] <- "long"

#Icons
greenIcon <- makeIcon(
  iconUrl = "https://cdn.rawgit.com/pointhi/leaflet-color-markers/master/img/marker-icon-2x-green.png",
  iconWidth = 25, iconHeight = 41,
  iconAnchorX = 12, iconAnchorY = 41
)

redIcon <- makeIcon(
  iconUrl = "https://cdn.rawgit.com/pointhi/leaflet-color-markers/master/img/marker-icon-2x-red.png",
  iconWidth = 25, iconHeight = 41,
  iconAnchorX = 12, iconAnchorY = 41
)

orangeIcon <- makeIcon(
  iconUrl = "https://cdn.rawgit.com/pointhi/leaflet-color-markers/master/img/marker-icon-2x-orange.png",
  iconWidth = 25, iconHeight = 41,
  iconAnchorX = 12, iconAnchorY = 41
)
```

```{r}
nysocializing <- ny %>% 
  filter(category == "socializing")

nylanguage <- ny %>% 
  filter(category == "language/ethnic identity")

nytech <- ny %>% 
  filter(category == "tech")

nysports <- ny %>% 
  filter(category == "sports/recreation")
```

```{r}
#Hartford
ctsocializing <- ha %>% 
  filter(category == "socializing")

ctlanguage <- ha %>% 
  filter(category == "language/ethnic identity")

cttech <- ha %>% 
  filter(category == "tech")

ctsports <- ha %>% 
  filter(category == "sports/recreation")
```

```{r}
#Boston
bosocializing <- bo %>% 
  filter(category == "socializing")

bolanguage <- bo %>% 
  filter(category == "language/ethnic identity")

botech <- bo %>% 
  filter(category == "tech")

bosports <- bo %>% 
  filter(category == "sports/recreation")
```

```{r}
#Charlotte
chsocializing <- ch %>% 
  filter(category == "socializing")

chlanguage <- ch %>% 
  filter(category == "language/ethnic identity")

chtech <- ch %>% 
  filter(category == "tech")

chsports <- ch %>% 
  filter(category == "sports/recreation")
```

```{r}
#creates df topics with number of groups per topic (fix this)
mostgroups<- function(data){
  topics <-data %>% 
  group_by(category) %>% 
  summarise(group_tot = n()) %>% 
  arrange(desc(group_tot));topics %>% 
    head(10)
}

chgroups<-mostgroups(ch)
nygroups<-mostgroups(ny)
bogroups<-mostgroups(bo)
hagroups<-mostgroups(ha)

topcatbygroup<-function(x){ggplot(data=x, aes(x=reorder(category, group_tot), y=group_tot))+geom_bar(stat="identity", aes(fill=group_tot)) +coord_flip()+ylab("Total groups")+xlab("Category")+scale_fill_continuous(name="total groups per category")
}




```

## Scenario

- Just moved into a new town, looking to meet new people!
- What are some of the popular events in the area?
- Bullet 3

How can we measure category popularity? 

## Methods

- Scraped live group and event data from a Meetup API
- Cities: Boston, Charlotte, Hartford, and New York
- Radius 10 miles 
- Python and R
- Converted html data to csv
- Ran summary statistics on groups and membership
- Determined the most popular categories per city based on each criteria
- Made a map to see if any patterns appeared with regards to location



## Categories
```{r}
unique(ch$category)
```

##New York
```{r}
topcatbygroup(nygroups)+labs(title = "NY top categories by group number")
# map of NY with events as category
NY  <- leaflet() %>%
  addTiles() %>%  
  #markers(Hartford)# Add default OpenStreetMap map tiles
  addMarkers(data=nysocializing, popup="social",icon=orangeIcon) %>% 
  addMarkers(data=nylanguage, popup="language",icon=greenIcon) %>% 
  addMarkers(data=nysports, popup="sports",icon=redIcon) %>% 
  addMarkers(data=nytech, popup="tech")
NY
```

## Hartford
```{r}
topcatbygroup(hagroups)+labs(title = "Hartford top categories by group number")
# map of Hartford
hartfordmap  <- leaflet() %>%
  addTiles() %>%  
  #markers(Hartford)# Add default OpenStreetMap map tiles
  addMarkers(data=ctsocializing, popup="social",icon=orangeIcon) %>% 
  addMarkers(data=ctlanguage, popup="language",icon=greenIcon) %>% 
  addMarkers(data=ctsports, popup="sports",icon=redIcon) %>% 
  addMarkers(data=cttech, popup="tech")
hartfordmap
```

## Boston
```{r}
topcatbygroup(bogroups)+labs(title = "Boston top categories by group number")
# map of Boston
bostonmap  <- leaflet() %>%
  addTiles() %>%  
  #markers(Hartford)# Add default OpenStreetMap map tiles
  addMarkers(data=bosocializing, popup="social",icon=orangeIcon) %>% 
  addMarkers(data=bolanguage, popup="language",icon=greenIcon) %>% 
  addMarkers(data=bosports, popup="sports",icon=redIcon)%>% 
  addMarkers(data=botech, popup="tech")
bostonmap
```

## Charlotte
```{r}
topcatbygroup(chgroups)+ labs(title = "Charlotte top categories by group number")
# map of Charlotte
charlottemap  <- leaflet() %>%
  addTiles() %>%  
  #markers(Hartford)# Add default OpenStreetMap map tiles
  addMarkers(data=chsocializing, popup="social",icon=orangeIcon) %>% 
  addMarkers(data=chlanguage, popup="language",icon=greenIcon) %>% 
  addMarkers(data=chsports, popup="sports",icon=redIcon) %>% 
  addMarkers(data=chtech, popup="tech")
charlottemap
```
